A formal approach but practical approach in train regulation

### 2025-06-06 paper/main.tex
nouvelle photo de la maquette

 The customer IT is deported from the infrastructure (thus the cloud).  It is itself composed of three machines: one for the station screens, one for the databases and a final orchestrator. On the orchestrator, there are two main services: we have a web-service (with front and backend, on the right) and the general route scheduler.  Our model is completely automatic, no manual intervention is needed apart from minor electrical/mechanical problems that come with our scale model.

\begin{wrapfigure}[8]{r}{0.28\textwidth}
 \begin{minipage}{0.28\textwidth}
        \centering
        \vspace{-10mm}
\includegraphics[height=50mm]{maquette.png}
    \end{minipage}
\end{wrapfigure}

@@

Routes are not computed in advance. The schedule is renewed every "day"\footnote{We use a time scale factor: one of our "day" corresponds to 20 minutes in real time.}  and we introduce some randomness in the process: some trains are inserted, some trains departure/destination may change, and so on. Finally, in our model, we distinguish freight and  passengers routes giving priority to the latter. Routes are recomputed each time a train as finished its duty.

 Now, we can enter in more details about how the train regulation works. First, we have sensors on the rails at the two ends of each block. Accordingly,  we can catch train entrances within blocks. We make the hypothesis that this task is performed without errors. Second, the switches can be swapped from one position to the other, again, we suppose it is done without fault. Our method could cope such issues, but we leave that for future work.

@@

 All these operations are done by what we call  \emph{orders}. Roughly speaking, trains Orders have the shape "Start in direction Until position". Regulator orders are: XXX.

>>>>

 The customer IT is deported from the infrastructure (thus the cloud).  It is itself composed of three machines: one for the station screens (on the right), one for the databases and a final orchestrator. On the orchestrator, there are two main services: we have a web-service (with front and backend) and the general route scheduler.  Our model is completely automatic, no manual intervention is needed apart from minor electrical/mechanical problems that come with our scale model.

\begin{wrapfigure}[8]{r}{0.28\textwidth}
 \begin{minipage}{0.28\textwidth}
        \centering
        \vspace{-8mm}
\includegraphics[height=30mm]{maquette.png}
    \end{minipage}
\end{wrapfigure}

@@

Routes are not computed in advance. The schedule is renewed every "day"\footnote{We use a time scale factor: one of our "day" corresponds to 20 minutes in real time.}  and we introduce some randomness in the process: around some routine daily planning, some trains are inserted/deleted, some trains departure/destination may change, and so on. We simulate also delays. Finally, in our model, we distinguish freight and  passengers routes giving priority to the latter. Routes are recomputed each time a train as finished its duty. The general motivation of this paper is to propose a scheduling solution that takes into account the distributed nature of the system, that is reliable and does not suffer from interlocking.

We can now describe in more detail the working assumptions we are making about planning.  First, we have sensors on the rails at the two ends of each block. Accordingly,  we can catch train entrances within blocks. We make the hypothesis that this task is performed without errors. Second, the switches can be swapped from one position to the other, again, we suppose it is done without fault. Our method could cope such issues, but we leave that for future work.

@@

 Parler de la stratégie, du modèle générale. All these operations are done by what we call  \emph{orders}. Roughly speaking, trains Orders have the shape "Start in direction Until position". Regulator orders are: XXX.
